Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
It's technically true to many OOM of precision
Small changes

These simulations contain dark matter particles of mass $\sim35,000\,\Msun$,
gas particles of mass $\sim 7000$ to $20,000\,\Msun$, and star particles
of mass $\sim 5000 \text{--} 7000\,
\Msun$,\footnote{In fact, the simulation \mi\ contained a gas
splitting bug which causes a small number of gas and star particles to have
larger than typical masses. These constitute only $\sim0.2\%$ of the star
particles in the $\z=0$ snapshots, and are only a factor of a few more massive
than typical star particles. Since our results are broadly consistent between
the three simulations, we ignore this minor complication.} with the lower end
coming from stellar evolution \citep{2018arXiv180610564S}. Softening lengths
for dark matter and star particles are fixed at $112\,\pc$ and $11.2\,\pc$,
respectively.\footnote{This is $2.8$ times the often-quoted
Plummer-equivalent.} The gas softening length is adaptive, but at $z=0$ the
median softening length for cold ($T < 10^4\,\text{K}$) gas particles around
roughly solar positions (with cylindrical radii within $500\,\pc$ of
$8.2\,\kpc$ and $\abs{z}<1\,\kpc$) is $12.4, 12.5, 10.3\,\pc$ for \mi , \mf ,
and \mm , respectively. These values are summarized in Table
\ref{tab:scale_height}.

\begin{deluxetable*}{cccccc}
\tablecaption{Stellar disk scale heights of the real Milky Way and the
simulated galaxies considered in this work.\label{tab:scale_height}}
\tablehead{\colhead{galaxy} & \colhead{cold\tablenotemark{a} gas disk} & \colhead{stellar thin disk} & \colhead{stellar thick disk} & \colhead{cold gas softening length} & \colhead{stellar softening length} \\ 
\colhead{} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} } 
\startdata
MW\tablenotemark{b} & 40 & 300 & 900 & \nodata & \nodata \\
\mi\tablenotemark{c} & 800\tablenotemark{d} & 480 & 2000 & 12.4 & 11.2 \\
\mf\tablenotemark{c} & 360 & 440 & 1280 & 12.5 & 11.2 \\
\mm\tablenotemark{c} & 250 & 290 & 1030 &10.3 & 11.2 \\
\enddata
% \tablerefs{\citet{2016ARAA..54..529B,2018arXiv180610564S,2008ApJ...673..864J}}
\tablenotetext{a}{$T<1000$ K}
\tablenotetext{b}{\citet{2008ApJ...673..864J,2016ARAA..54..529B}}
\tablenotetext{c}{\citet{2018arXiv180610564S}}
\tablenotetext{d}{The azimuthally averaged gas vertical density profile in
m12i is nearly constant to this height, though individual regions show smaller
scale heights and dense clouds.}
\end{deluxetable*}

@@

Figure~\ref{fig:Rn_mc} is most informative for the thin orbit (\thincolor).
The neighborhood around $\sim100\Msun$ clusters can be as small as
$\sim300\,\pc$ but up to $\sim1.2\,\kpc$ for \mi\ and \mf , though the
situation is marginally better for \mm\ with values ranging from
$\sim0.8\,\kpc$ to $\sim3\,\kpc$. The neighborhood values steadily increase
with $m_c$, topping out at $\sim5\,\kpc$ for $\sim10^4\,\Msun$ clusters in
\mi\ and \mf . In \mm , the neighborhood value reaches the maximum allowed of
$16.4\,\kpc$ for clusters of mass $\sim800\,\Msun$. The interpretation of this
is that the expected action space dispersion is so high for such high mass
clusters that the measured $z$~offset is not large enough throughout the
entire galaxy to be important.

>>>>

These simulations contain dark matter particles of mass $\sim35,000\,\Msun$,
gas particles of mass $\sim 7000$ to $20,000\,\Msun$, and star particles
of mass $\sim 5000 \text{--} 7000\,
\Msun$,\footnote{In fact, the simulation \mi{} contained a gas
splitting bug which causes a small number of gas and star particles to have
larger than typical masses. These constitute only $\sim0.2\%$ of the star
particles in the $\z=0$ snapshots, and are only a factor of a few more massive
than typical star particles. Since our results are broadly consistent between
the three simulations, we ignore this minor complication.} with the lower end
coming from stellar evolution \citep{2018arXiv180610564S}. Softening lengths
for dark matter and star particles are fixed at $112\,\pc$ and $11.2\,\pc$,
respectively.\footnote{This is $2.8$ times the often-quoted
Plummer-equivalent.} The gas softening length is adaptive, but at $z=0$ the
median softening length for cold ($T < 10^4\,\text{K}$) gas particles around
roughly solar positions (with cylindrical radii within $500\,\pc$ of
$8.2\,\kpc$ and $\abs{z}<1\,\kpc$) is $12.4, 12.5, 10.3\,\pc$ for \mi , \mf ,
and \mm , respectively. These values are summarized in
Table~\ref{tab:scale_height}.

\begin{deluxetable*}{cccccc}
\tablecaption{Stellar disk scale heights of the real Milky Way and the
simulated galaxies considered in this work.\label{tab:scale_height}}
\tablehead{\colhead{galaxy} & \colhead{cold\tablenotemark{a} gas disk} & \colhead{stellar thin disk} & \colhead{stellar thick disk} & \colhead{cold gas softening length} & \colhead{stellar softening length} \\ 
\colhead{} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} } 
\startdata
MW\tablenotemark{b} & 40 & 300 & 900 & 0 & 0 \\
\mi\tablenotemark{c} & 800\tablenotemark{d} & 480 & 2000 & 12.4 & 11.2 \\
\mf\tablenotemark{c} & 360 & 440 & 1280 & 12.5 & 11.2 \\
\mm\tablenotemark{c} & 250 & 290 & 1030 &10.3 & 11.2 \\
\enddata
% \tablerefs{\citet{2016ARAA..54..529B,2018arXiv180610564S,2008ApJ...673..864J}}
\tablenotetext{a}{$T<1000$ K}
\tablenotetext{b}{\citet{2008ApJ...673..864J,2016ARAA..54..529B}}
\tablenotetext{c}{\citet{2018arXiv180610564S}}
\tablenotetext{d}{The azimuthally averaged gas vertical density profile in
m12i is nearly constant to this height, though individual regions show smaller
scale heights and dense clouds.}
\end{deluxetable*}

@@

Figure~\ref{fig:Rn_mc} is most informative for the thin orbit (\thincolor).
The neighborhood around $\sim100\Msun$ clusters can be as small as
$\sim300\,\pc$ but up to $\sim1.2\,\kpc$ for \mi{} and \mf{}, though the
situation is marginally better for \mm{} with values ranging from
$\sim0.8\,\kpc$ to $\sim3\,\kpc$. The neighborhood values steadily increase
with $m_c$, topping out at $\sim5\,\kpc$ for $\sim10^4\,\Msun$ clusters in
\mi{} and \mf{}. In \mm{}, the neighborhood value reaches the maximum allowed of
$16.4\,\kpc$ for clusters of mass $\sim800\,\Msun$. The interpretation of this
is that the expected action space dispersion is so high for such high mass
clusters that the measured $z$~offset is not large enough throughout the
entire galaxy to be important.
